{\large The Mass / A Missa}

\vspace{10pt}

\raggedright
{\bf In English:}
Welcome to our wedding! If you are familiar with the Catholic Mass, in any country, you will find these prayers familiar to you. All Masses follow the same structure in all churches around the world. Please join in the the responses in whatever language you prefer. If you are not familiar with the Mass, please follow the lead of those around you however you feel comfortable.

\vspace{10pt}

\raggedright
{\bf Em Português:} Bem-vindo ao nosso casamento! Se você está familiar com a missa católica, vais encontrar estas orações familiar tambêm. Todas as Missas no mundo seguem a mesma estrutura em todas as igrejas do mundo. Por favor, junte connosco nas respostas com qualquer idioma preferes. Se não estás familiar com a Missa, segue o exemplo dos demais como sentires comodo.


\vspace{20pt}

\centering

{\large Entrance Hymn / ???}
\footnotesize

\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}                  
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}} 


\begin{longtable}{L{2in}R{2in}}
  {\bf Canto em Português:}&{\bf Translation in English:}\\
  
  Ó Senhora minha & {\it Oh my lady} \\  
	ó minha Mãe & {\it o my Mother} \\
	eu me ofereço toda a vós & {\it I offer myself totally to you}\\ 
  e em prova da minha devoção para convosco & {\it and in proof of my devotion to you}\\
  Vos consagro neste dia e para sempre & {\it I consecrate to you this day and forever}\\
  os meus olhos, os meus ouvidos & {\it my eyes, my ears}\\
  a minha boca, o meu coração & {\it my mouth, my heart}\\
  e inteiramente todo o meu ser & {\it and entirely all of my being}\\
  E porque assim sou vossa & {\it And because I am yours}\\
  ó incomparável Mãe & {\it oh incomparable Mother}, \\ 
  guardai-me e defendei-me como propriedade vossa & {\it guard me and defend me as your own}\\
  Lembrai-vos que vos pertenço & {\it remember that I belong to you}\\
  terna Mãe & {\it caring Mother}\\ 
  Senhora nossa & {\it our Lady}\\
  Ah, guardai-me e defendei-me como coisa própria vossa & {\it Ah, guard me and defend me as your own}\\
  \end{longtable}
